A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-05-31 bioc-workflow.Rmd
code for classification

# Supervised machine learning
Supervised machine learning, also known as classification, is an essential tool for the assignment of proteins to distinct sub-cellular niches. Using a set of labelled training examples i.e. markers, we can train a machine learning classifier to learn a mapping between the data i.e. the quantitative protein profiles, and the known localisation. The trained classifier can then be used to predict the localisation of a protein of unknown localisation, based on its observed protein profile. To date, this method has been extensively used in spatial quantitative proteomics to assign thousands of proteins to distinct sub-cellular niches [@hyper; @Groen:2014; @trotter; @Hall:2009; @Dunkley:2006; @Tan:2009]

>>>>

# Supervised machine learning

Supervised machine learning, also known as classification, is an essential tool for the assignment of proteins to distinct sub-cellular niches. Using a set of labelled training examples i.e. markers, we can train a machine learning classifier to learn a mapping between the data i.e. the quantitative protein profiles, and a known localisation. The trained classifier can then be used to predict the localisation of a protein of unknown localisation, based on its observed protein profile. To date, this method has been extensively used in spatial quantitative proteomics to assign thousands of proteins to distinct sub-cellular niches [@hyper; @Groen:2014; @trotter; @Hall:2009; @Dunkley:2006; @Tan:2009]. In the below code chunk we demonstrate how to run a typical classification analysis.

```{r loadpdRes, include=FALSE}
pdRes <- lopit2016
load("Data/fusionparams.rda")
```
```{r optimise, eval=FALSE}
w <- table(fData(pdRes)[, "SVM.marker.set"])
w <- 1/w[names(w) != "unknown"]

params <- svmOptimisation(pdRes, fcol = "SVM.marker.set",
                          times = 100, xval = 5,
                          class.weights = w,
                          verbose = TRUE)
```
```{r visualiseOpt}
plot(params)
levelPlot(params)
(best <- getParams(params))
```
```{r classify, eval=TRUE}
svmRes <- svmClassification(pdRes, params,
                            class.weights = w,
                            fcol = "SVM.marker.set")
```
